From Reversible Programs to \\ Univalent Universes and Back

### 2021-07-05 Pi+/paper/finite.tex
Change the coxeter relation symbols

\begin{proposition}~\label{prop:coxlongcox}
  $\cox*$ and $\longcox*$ are equivalent in the following sense: for every $w$ and $v$, $w \cox* v$ iff there is a $u$
  such that $w \longcox* u$ and $v \longcox* u$.
\end{proposition}

>>>>

\begin{proposition}
  \label{prop:coxlongcox}
  The relations $\cox*$ and $\longcox*$ are equivalent in the following sense: for every $w$ and $v$, $w \cox* v$ iff
  there is a $u$ such that $w \longcox* u$ and $v \longcox* u$.
\end{proposition}
